Understanding meta-analysis through data simulation with applications to power analysis

### 2023-09-26 documents/output/paper.tex
final fix

@@

\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs

@@

  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}

@@

  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}

@@

\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}

@@

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

@@

\hypertarget{meta-analysis-introduction}{%
\subsection{Meta-analysis introduction}\label{meta-analysis-introduction}}

@@

\hypertarget{effect-size-and-variance}{%
\subsubsection{Effect size and variance}\label{effect-size-and-variance}}

@@

\hypertarget{equal-vs-fixed-vs-random-effects-model}{%
\subsubsection{Equal vs fixed vs random-effects model}\label{equal-vs-fixed-vs-random-effects-model}}

@@

\hypertarget{simulation}{%
\section{Simulation}\label{simulation}}

\hypertarget{monte-carlo-simulations}{%
\subsection{Monte Carlo simulations}\label{monte-carlo-simulations}}

@@

\hypertarget{simulation-setup}{%
\subsection{Simulation setup}\label{simulation-setup}}

@@

  \CommentTok{\# sampling variance}
\NormalTok{  vi }\OtherTok{\textless{}{-}} \FunctionTok{var}\NormalTok{(yt)}\SpecialCharTok{/}\NormalTok{nt }\SpecialCharTok{+} \FunctionTok{var}\NormalTok{(yt)}\SpecialCharTok{/}\NormalTok{nc}

@@

\hypertarget{equal-effects-model}{%
\subsection{Equal-effects model}\label{equal-effects-model}}

@@

\caption{\label{tab:res-equal-effects}Summary of the simulated equal-effects model. The only estimated parameter is the average effect \(\theta\) (\(\beta\)) with the standard error, 95\% confidence interval, and the Wald z-test. The z-test evaluates the null hypothesis that the real effect equals zero.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.347 (SE = 0.056) & $[0.237, 0.456]$ & 6.223 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\end{tabular}
\end{table}

@@

\hypertarget{re-model}{%
\subsection{Random-effects model}\label{re-model}}

@@

\caption{\label{tab:res-random-effects}Summary of the simulated random-effects model: Compared to the equal-effects model, there are more parameters. The \(\beta\) is the average effect (\(\mu_{\theta}\)) with the standard error, 95\% confidence interval, and the Wald z-test. The \(\tau^{2}\) is the estimated heterogeneity and the \(I^{2}\) (explained in Section \ref{re-model}) represents the percentage of total variability due to between-study heterogeneity.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.394 (SE = 0.110) & $[0.179, 0.609]$ & 3.596 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2 = 0.262$ ($SE = 0.095$)}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 73.480\%$}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:res-random-effects-i2}Summary of the random-effects model fixing the \(I^2\) value. Parameters are the same as described in Table \ref{tab:res-random-effects}.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.300 (SE = 0.071) & $[0.160, 0.440]$ & 4.201 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2 = 0.087$ ($SE = 0.040$)}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 57.904\%$}\\
\end{tabular}
\end{table}

@@

\hypertarget{metareg}{%
\subsection{Meta-regression}\label{metareg}}

@@

\hypertarget{meta-regression-with-a-categorical-moderator}{%
\subsubsection{Meta-regression with a categorical moderator}\label{meta-regression-with-a-categorical-moderator}}

@@

\caption{\label{tab:res-meta-reg-dummy}Summary of the \emph{random-effect} model with a categorical predictor (lab vs online experiments). The \texttt{intercept} is the average effect for lab-based experiments and \texttt{exponline} is the difference between lab-based and online experiments. The \(R^2\) is the percentage of explained heterogeneity and \(\tau^2_r\) is the estimated residual heterogeneity. Other parameters are the same as the standard \emph{random-effect} model (see Table \ref{tab:res-random-effects}).}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
intercept & 0.038 (SE = 0.101) & $[-0.161, 0.236]$ & 0.372 & 0.710\\
exponline & 0.323 (SE = 0.143) & $[0.043, 0.602]$ & 2.263 & 0.024\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2_r = 0.087$ ($SE = 0.041$)}\\
\multicolumn{5}{l}{\textsuperscript{} $R^2 = 20.659\%$}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 57.741\%$}\\
\end{tabular}
\end{table}

@@

\hypertarget{meta-regression-with-a-numerical-moderator}{%
\subsubsection{Meta-regression with a numerical moderator}\label{meta-regression-with-a-numerical-moderator}}

@@

\hypertarget{assessing-the-impact-of-beta_1}{%
\paragraph{\texorpdfstring{Assessing the impact of \(\beta_1\)}{Assessing the impact of \textbackslash beta\_1}}\label{assessing-the-impact-of-beta_1}}

@@

\hypertarget{simulating-using-r2}{%
\paragraph{\texorpdfstring{Simulating using \(R^2\)}{Simulating using R\^{}2}}\label{simulating-using-r2}}

@@

\caption{\label{tab:res-meta-reg-numerical-r2}Summary of the \emph{random-effects} model fixing the \(R^{2}\) value. The \texttt{intercept} is the effect size for the average \texttt{age} (given that age is mean-centered). The \texttt{age0} parameter is the slope between \texttt{age} and the effect size interpreted as an increase in effect size for a unit increase in the average age. Other parameters are the same as described in Table \ref{tab:res-random-effects} and \ref{tab:res-meta-reg-dummy}.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
intercept & 0.339 (SE = 0.051) & $[0.239, 0.439]$ & 6.643 & < 0.001\\
age0 & 0.168 (SE = 0.051) & $[0.067, 0.268]$ & 3.272 & 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 100$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2_r = 0.197$ ($SE = 0.037$)}\\
\multicolumn{5}{l}{\textsuperscript{} $R^2 = 11.029\%$}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 76.611\%$}\\
\end{tabular}
\end{table}

@@

\hypertarget{power-analysis}{%
\section{Power Analysis}\label{power-analysis}}

@@

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

@@

\hypertarget{acknowledgments}{%
\subsubsection*{Acknowledgments}\label{acknowledgments}}
\addcontentsline{toc}{subsubsection}{Acknowledgments}

@@

\hypertarget{conflicts-of-interest}{%
\subsubsection*{Conflicts of Interest}\label{conflicts-of-interest}}
\addcontentsline{toc}{subsubsection}{Conflicts of Interest}

@@

\hypertarget{data-materials-and-online-resources}{%
\subsubsection*{Data, materials, and online resources}\label{data-materials-and-online-resources}}
\addcontentsline{toc}{subsubsection}{Data, materials, and online resources}

@@

\hypertarget{supplemental-material}{%
\subsubsection*{Supplemental Material}\label{supplemental-material}}
\addcontentsline{toc}{subsubsection}{Supplemental Material}

@@

\hypertarget{prior-versions}{%
\subsubsection*{Prior versions}\label{prior-versions}}
\addcontentsline{toc}{subsubsection}{Prior versions}

@@

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2022). \emph{Papaja: Prepare american psychological association journal articles with r markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\leavevmode\vadjust pre{\hypertarget{ref-Berkhout2023-fj}{}}%
Berkhout, S. W., Haaf, J. M., Gronau, Q. F., Heck, D. W., \& Wagenmakers, E.-J. (2023). A tutorial on bayesian model-averaged meta-analysis in {JASP}. \emph{Behav. Res. Methods}. \url{https://doi.org/10.3758/s13428-023-02093-6}

\leavevmode\vadjust pre{\hypertarget{ref-Blazquez-Rincon2023-kp}{}}%
Blázquez-Rincón, D., Sánchez-Meca, J., Botella, J., \& Suero, M. (2023). Heterogeneity estimation in meta-analysis of standardized mean differences when the distribution of random effects departs from normal: A monte carlo simulation study. \emph{BMC Med. Res. Methodol.}, \emph{23}(1), 19. \url{https://doi.org/10.1186/s12874-022-01809-0}

\leavevmode\vadjust pre{\hypertarget{ref-Borenstein2009-mo}{}}%
Borenstein, M., Hedges, L. V., Higgins, J. P. T., \& Rothstein, H. R. (2009). \emph{Introduction to {Meta-Analysis}}. \url{https://doi.org/10.1002/9780470743386}

\leavevmode\vadjust pre{\hypertarget{ref-Cohen1988-ad}{}}%
Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). Routledge. \url{https://doi.org/10.4324/9780203771587}

\leavevmode\vadjust pre{\hypertarget{ref-DeBruine2021-id}{}}%
DeBruine, L. M., \& Barr, D. J. (2021). Understanding {Mixed-Effects} models through data simulation. \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(1), 2515245920965119. \url{https://doi.org/10.1177/2515245920965119}

\leavevmode\vadjust pre{\hypertarget{ref-Gelman2006-pc}{}}%
Gelman, A., \& Hill, J. (2006). \emph{Data analysis using regression and {Multilevel/Hierarchical} models}. Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511790942}

\leavevmode\vadjust pre{\hypertarget{ref-Gelman2020-tg}{}}%
Gelman, A., Hill, J., \& Vehtari, A. (2020). \emph{Regression and other stories}. Cambridge University Press. \url{https://doi.org/10.1017/9781139161879}

\leavevmode\vadjust pre{\hypertarget{ref-Gentle2009-cj}{}}%
Gentle, J. E. (2009). Monte carlo methods for statistical inference. In J. E. Gentle (Ed.), \emph{Computational statistics} (pp. 417--433). New York, NY: Springer New York. \url{https://doi.org/10.1007/978-0-387-98144-4/_11}

\leavevmode\vadjust pre{\hypertarget{ref-Gronau2021-do}{}}%
Gronau, Q. F., Heck, D. W., Berkhout, S. W., Haaf, J. M., \& Wagenmakers, E.-J. (2021). A primer on bayesian model-averaged meta-analysis. \emph{Adv. Methods Pract. Psychol. Sci.}, \emph{4}(3), 251524592110312. \url{https://doi.org/10.1177/25152459211031256}

\leavevmode\vadjust pre{\hypertarget{ref-Harrer2019-rl}{}}%
Harrer, M., Cuijpers, P., \& Ebert, D. (2019). \emph{Doing {Meta-Analysis} in {R}}. \url{https://doi.org/10.5281/zenodo.2551803}

\leavevmode\vadjust pre{\hypertarget{ref-Harrer2021-bz}{}}%
Harrer, M., Cuijpers, P., Furukawa, T. A., \& Ebert, D. D. (2021). \emph{Doing {Meta-Analysis} with r: A {Hands-On} guide}. CRC Press.

\leavevmode\vadjust pre{\hypertarget{ref-Hedges1981-za}{}}%
Hedges, L. V. (1981). Distribution theory for glass's estimator of effect size and related estimators. \emph{J. Educ. Behav. Stat.}, \emph{6}(2), 107--128. \url{https://doi.org/10.3102/10769986006002107}

\leavevmode\vadjust pre{\hypertarget{ref-Hedges1989-ip}{}}%
Hedges, L. V. (1989). An unbiased correction for sampling error in validity generalization studies. \emph{J. Appl. Psychol.}, \emph{74}(3), 469--477. \url{https://doi.org/10.1037/0021-9010.74.3.469}

\leavevmode\vadjust pre{\hypertarget{ref-Hedges1998-uo}{}}%
Hedges, L. V., \& Vevea, J. L. (1998). Fixed- and random-effects models in meta-analysis. \emph{Psychol. Methods}, \emph{3}(4), 486--504. \url{https://doi.org/10.1037/1082-989X.3.4.486}

\leavevmode\vadjust pre{\hypertarget{ref-van-den-Heuvel2020-rv}{}}%
Heuvel, E. R. van den, Almalik, O., \& Zhan, Z. (2020). \emph{Simulation models for aggregated data meta-analysis: Evaluation of pooling effect sizes and publication biases}. Retrieved from \url{https://arxiv.org/abs/2009.06305}

\leavevmode\vadjust pre{\hypertarget{ref-Higgins2002-fh}{}}%
Higgins, J. P. T., \& Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. \emph{Stat. Med.}, \emph{21}(11), 1539--1558. \url{https://doi.org/10.1002/sim.1186}

\leavevmode\vadjust pre{\hypertarget{ref-Ingalls2011-xt}{}}%
Ingalls, R. G. (2011). Introduction to simulation. \emph{Proceedings of the 2011 Winter Simulation Conference ({WSC})}, 1374--1388. ieeexplore.ieee.org. \url{https://doi.org/10.1109/WSC.2011.6147858}

\leavevmode\vadjust pre{\hypertarget{ref-Jackson2017-dv}{}}%
Jackson, D., \& Turner, R. (2017). Power analysis for random-effects meta-analysis. \emph{Res. Synth. Methods}, \emph{8}(3), 290--302. \url{https://doi.org/10.1002/jrsm.1240}

\leavevmode\vadjust pre{\hypertarget{ref-Klein2018-he}{}}%
Klein, R. A., Vianello, M., Hasselman, F., Adams, B. G., Adams, R. B., Jr, Alper, S., \ldots{} Nosek, B. A. (2018). Many labs 2: Investigating variation in replicability across samples and settings. \emph{Adv. Methods Pract. Psychol. Sci.}, \emph{1}(4), 443--490. \url{https://doi.org/10.1177/2515245918810225}

\leavevmode\vadjust pre{\hypertarget{ref-Knapp2003-qx}{}}%
Knapp, G., \& Hartung, J. (2003). Improved tests for a random effects meta-regression with a single covariate. \emph{Stat. Med.}, \emph{22}(17), 2693--2710. \url{https://doi.org/10.1002/sim.1482}

\leavevmode\vadjust pre{\hypertarget{ref-Laird1990-ro}{}}%
Laird, N. M., \& Mosteller, F. (1990). Some statistical methods for combining experimental results. \emph{Int. J. Technol. Assess. Health Care}, \emph{6}(1), 5--30. \url{https://doi.org/10.1017/s0266462300008916}

\leavevmode\vadjust pre{\hypertarget{ref-Lakens2013-eq}{}}%
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and {ANOVAs}. \emph{Front. Psychol.}, \emph{4}, 863. \url{https://doi.org/10.3389/fpsyg.2013.00863}

\leavevmode\vadjust pre{\hypertarget{ref-Lipsey2001-vp}{}}%
Lipsey, M. W., \& Wilson, D. B. (2001). Practical meta-analysis. \emph{Applied Social Research Methods Series; Vol 49.}, \emph{247}.

\leavevmode\vadjust pre{\hypertarget{ref-Lopez-Lopez2014-it}{}}%
López-López, J. A., Marı́n-Martı́nez, F., Sánchez-Meca, J., Van den Noortgate, W., \& Viechtbauer, W. (2014). Estimation of the predictive power of the model in mixed-effects meta-regression: A simulation study. \emph{Br. J. Math. Stat. Psychol.}, \emph{67}(1), 30--48. \url{https://doi.org/10.1111/bmsp.12002}

\leavevmode\vadjust pre{\hypertarget{ref-r-lang}{}}%
R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing.

>>>>

% definitions for citeproc citations
\NewDocumentCommand\citeproctext{}{}
\NewDocumentCommand\citeproc{mm}{%
  \begingroup\def\citeproctext{#2}\cite{#1}\endgroup}
 % allow citations to break across lines
 \let\@cite@ofmt\@firstofone
 % avoid brackets around text for \cite:
 \def\@biblabel#1{}
 \def\@cite#1#2{{#1\if@tempswa , #2\fi}}

@@

\newenvironment{CSLReferences}[2] % #1 hanging-indent, #2 entry-spacing
 {\begin{list}{}{%
  \setlength{\itemindent}{0pt}
  \setlength{\leftmargin}{0pt}
  \setlength{\parsep}{0pt}

@@

   \setlength{\leftmargin}{\cslhangindent}
   \setlength{\itemindent}{-1\cslhangindent}

@@

  \setlength{\itemsep}{#2\baselineskip}}}
 {\end{list}}

@@

\newcommand{\CSLBlock}[1]{\hfill\break#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{\strut#1\strut}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{\strut#1\strut}}

@@

\section{Introduction}\label{introduction}

@@

\subsection{Meta-analysis introduction}\label{meta-analysis-introduction}

@@

\subsubsection{Effect size and variance}\label{effect-size-and-variance}

@@

\subsubsection{Equal vs fixed vs random-effects model}\label{equal-vs-fixed-vs-random-effects-model}

@@

\section{Simulation}\label{simulation}

\subsection{Monte Carlo simulations}\label{monte-carlo-simulations}

@@

\subsection{Simulation setup}\label{simulation-setup}

@@

  \CommentTok{\# sampling variance}
\NormalTok{  vi }\OtherTok{\textless{}{-}} \FunctionTok{var}\NormalTok{(yt)}\SpecialCharTok{/}\NormalTok{nt }\SpecialCharTok{+} \FunctionTok{var}\NormalTok{(yc)}\SpecialCharTok{/}\NormalTok{nc}

@@

\subsection{Equal-effects model}\label{equal-effects-model}

@@

\caption{\label{tab:res-equal-effects}Summary of the simulated equal-effects model. The only estimated parameter is the average effect \(\theta\) (\(\beta\)) with the standard error, 95\% confidence interval, and the Wald z-test. The z-test evaluates the null hypothesis that the real effect equals zero.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.339 (SE = 0.057) & $[0.228, 0.451]$ & 5.959 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\end{tabular}
\end{table}

@@

\subsection{Random-effects model}\label{re-model}

@@

\caption{\label{tab:res-random-effects}Summary of the simulated random-effects model: Compared to the equal-effects model, there are more parameters. The \(\beta\) is the average effect (\(\mu_{\theta}\)) with the standard error, 95\% confidence interval, and the Wald z-test. The \(\tau^{2}\) is the estimated heterogeneity and the \(I^{2}\) (explained in Section \ref{re-model}) represents the percentage of total variability due to between-study heterogeneity.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.387 (SE = 0.107) & $[0.177, 0.597]$ & 3.616 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2 = 0.246$ ($SE = 0.090$)}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 71.925\%$}\\
\end{tabular}
\end{table}

@@

\caption{\label{tab:res-random-effects-i2}Summary of the random-effects model fixing the \(I^2\) value. Parameters are the same as described in Table \ref{tab:res-random-effects}.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
overall & 0.305 (SE = 0.072) & $[0.164, 0.447]$ & 4.226 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2 = 0.091$ ($SE = 0.041$)}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 58.479\%$}\\
\end{tabular}
\end{table}

@@

\subsection{Meta-regression}\label{metareg}

@@

\subsubsection{Meta-regression with a categorical moderator}\label{meta-regression-with-a-categorical-moderator}

@@

\caption{\label{tab:res-meta-reg-dummy}Summary of the \emph{random-effect} model with a categorical predictor (lab vs online experiments). The \texttt{intercept} is the average effect for lab-based experiments and \texttt{exponline} is the difference between lab-based and online experiments. The \(R^2\) is the percentage of explained heterogeneity and \(\tau^2_r\) is the estimated residual heterogeneity. Other parameters are the same as the standard \emph{random-effect} model (see Table \ref{tab:res-random-effects}).}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
intercept & 0.043 (SE = 0.103) & $[-0.158, 0.244]$ & 0.42 & 0.674\\
exponline & 0.323 (SE = 0.144) & $[0.040, 0.606]$ & 2.24 & 0.025\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 30$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2_r = 0.091$ ($SE = 0.042$)}\\
\multicolumn{5}{l}{\textsuperscript{} $R^2 = 19.824\%$}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 58.323\%$}\\
\end{tabular}
\end{table}

@@

\subsubsection{Meta-regression with a numerical moderator}\label{meta-regression-with-a-numerical-moderator}

@@

\paragraph{\texorpdfstring{Assessing the impact of \(\beta_1\)}{Assessing the impact of \textbackslash beta\_1}}\label{assessing-the-impact-of-beta_1}

@@

\paragraph{\texorpdfstring{Simulating using \(R^2\)}{Simulating using R\^{}2}}\label{simulating-using-r2}

@@

\caption{\label{tab:res-meta-reg-numerical-r2}Summary of the \emph{random-effects} model fixing the \(R^{2}\) value. The \texttt{intercept} is the effect size for the average \texttt{age} (given that age is mean-centered). The \texttt{age0} parameter is the slope between \texttt{age} and the effect size interpreted as an increase in effect size for a unit increase in the average age. Other parameters are the same as described in Table \ref{tab:res-random-effects} and \ref{tab:res-meta-reg-dummy}.}
\centering
\fontsize{9}{11}\selectfont
\begin{tabular}[t]{ccccc}
\toprule
 & $\beta$ & 95\% CI & z & p\\
\midrule
intercept & 0.340 (SE = 0.051) & $[0.240, 0.439]$ & 6.680 & < 0.001\\
age0 & 0.168 (SE = 0.051) & $[0.068, 0.269]$ & 3.296 & < 0.001\\
\bottomrule
\multicolumn{5}{l}{\textsuperscript{} $k = 100$}\\
\multicolumn{5}{l}{\textsuperscript{} $\tau^2_r = 0.194$ ($SE = 0.037$)}\\
\multicolumn{5}{l}{\textsuperscript{} $R^2 = 11.422\%$}\\
\multicolumn{5}{l}{\textsuperscript{} $I^2 = 75.417\%$}\\
\end{tabular}
\end{table}

@@

\section{Power Analysis}\label{power-analysis}

@@

\section{Conclusions}\label{conclusions}

@@

\subsubsection*{Acknowledgments}\label{acknowledgments}
\addcontentsline{toc}{subsubsection}{Acknowledgments}

@@

\subsubsection*{Conflicts of Interest}\label{conflicts-of-interest}
\addcontentsline{toc}{subsubsection}{Conflicts of Interest}

@@

\subsubsection*{Data, materials, and online resources}\label{data-materials-and-online-resources}
\addcontentsline{toc}{subsubsection}{Data, materials, and online resources}

@@

\subsubsection*{Supplemental Material}\label{supplemental-material}
\addcontentsline{toc}{subsubsection}{Supplemental Material}

@@

\subsubsection*{Prior versions}\label{prior-versions}
\addcontentsline{toc}{subsubsection}{Prior versions}

@@

\section*{References}\label{references}
\addcontentsline{toc}{section}{References}

\phantomsection\label{refs}
\begin{CSLReferences}{1}{0}
\bibitem[\citeproctext]{ref-R-papaja}
Aust, F., \& Barth, M. (2022). \emph{Papaja: Prepare american psychological association journal articles with r markdown}. Retrieved from \url{https://github.com/crsh/papaja}

\bibitem[\citeproctext]{ref-Berkhout2023-fj}
Berkhout, S. W., Haaf, J. M., Gronau, Q. F., Heck, D. W., \& Wagenmakers, E.-J. (2023). A tutorial on bayesian model-averaged meta-analysis in {JASP}. \emph{Behav. Res. Methods}. \url{https://doi.org/10.3758/s13428-023-02093-6}

\bibitem[\citeproctext]{ref-Blazquez-Rincon2023-kp}
Blázquez-Rincón, D., Sánchez-Meca, J., Botella, J., \& Suero, M. (2023). Heterogeneity estimation in meta-analysis of standardized mean differences when the distribution of random effects departs from normal: A monte carlo simulation study. \emph{BMC Med. Res. Methodol.}, \emph{23}(1), 19. \url{https://doi.org/10.1186/s12874-022-01809-0}

\bibitem[\citeproctext]{ref-Borenstein2009-mo}
Borenstein, M., Hedges, L. V., Higgins, J. P. T., \& Rothstein, H. R. (2009). \emph{Introduction to {Meta-Analysis}}. \url{https://doi.org/10.1002/9780470743386}

\bibitem[\citeproctext]{ref-Cohen1988-ad}
Cohen, J. (1988). \emph{Statistical power analysis for the behavioral sciences} (2nd ed.). Routledge. \url{https://doi.org/10.4324/9780203771587}

\bibitem[\citeproctext]{ref-DeBruine2021-id}
DeBruine, L. M., \& Barr, D. J. (2021). Understanding {Mixed-Effects} models through data simulation. \emph{Advances in Methods and Practices in Psychological Science}, \emph{4}(1), 2515245920965119. \url{https://doi.org/10.1177/2515245920965119}

\bibitem[\citeproctext]{ref-Gelman2006-pc}
Gelman, A., \& Hill, J. (2006). \emph{Data analysis using regression and {Multilevel/Hierarchical} models}. Cambridge University Press. \url{https://doi.org/10.1017/CBO9780511790942}

\bibitem[\citeproctext]{ref-Gelman2020-tg}
Gelman, A., Hill, J., \& Vehtari, A. (2020). \emph{Regression and other stories}. Cambridge University Press. \url{https://doi.org/10.1017/9781139161879}

\bibitem[\citeproctext]{ref-Gentle2009-cj}
Gentle, J. E. (2009). Monte carlo methods for statistical inference. In J. E. Gentle (Ed.), \emph{Computational statistics} (pp. 417--433). New York, NY: Springer New York. \url{https://doi.org/10.1007/978-0-387-98144-4/_11}

\bibitem[\citeproctext]{ref-Gronau2021-do}
Gronau, Q. F., Heck, D. W., Berkhout, S. W., Haaf, J. M., \& Wagenmakers, E.-J. (2021). A primer on bayesian model-averaged meta-analysis. \emph{Adv. Methods Pract. Psychol. Sci.}, \emph{4}(3), 251524592110312. \url{https://doi.org/10.1177/25152459211031256}

\bibitem[\citeproctext]{ref-Harrer2019-rl}
Harrer, M., Cuijpers, P., \& Ebert, D. (2019). \emph{Doing {Meta-Analysis} in {R}}. \url{https://doi.org/10.5281/zenodo.2551803}

\bibitem[\citeproctext]{ref-Harrer2021-bz}
Harrer, M., Cuijpers, P., Furukawa, T. A., \& Ebert, D. D. (2021). \emph{Doing {Meta-Analysis} with r: A {Hands-On} guide}. CRC Press.

\bibitem[\citeproctext]{ref-Hedges1981-za}
Hedges, L. V. (1981). Distribution theory for glass's estimator of effect size and related estimators. \emph{J. Educ. Behav. Stat.}, \emph{6}(2), 107--128. \url{https://doi.org/10.3102/10769986006002107}

\bibitem[\citeproctext]{ref-Hedges1989-ip}
Hedges, L. V. (1989). An unbiased correction for sampling error in validity generalization studies. \emph{J. Appl. Psychol.}, \emph{74}(3), 469--477. \url{https://doi.org/10.1037/0021-9010.74.3.469}

\bibitem[\citeproctext]{ref-Hedges1998-uo}
Hedges, L. V., \& Vevea, J. L. (1998). Fixed- and random-effects models in meta-analysis. \emph{Psychol. Methods}, \emph{3}(4), 486--504. \url{https://doi.org/10.1037/1082-989X.3.4.486}

\bibitem[\citeproctext]{ref-van-den-Heuvel2020-rv}
Heuvel, E. R. van den, Almalik, O., \& Zhan, Z. (2020). \emph{Simulation models for aggregated data meta-analysis: Evaluation of pooling effect sizes and publication biases}. Retrieved from \url{https://arxiv.org/abs/2009.06305}

\bibitem[\citeproctext]{ref-Higgins2002-fh}
Higgins, J. P. T., \& Thompson, S. G. (2002). Quantifying heterogeneity in a meta-analysis. \emph{Stat. Med.}, \emph{21}(11), 1539--1558. \url{https://doi.org/10.1002/sim.1186}

\bibitem[\citeproctext]{ref-Ingalls2011-xt}
Ingalls, R. G. (2011). Introduction to simulation. \emph{Proceedings of the 2011 Winter Simulation Conference ({WSC})}, 1374--1388. ieeexplore.ieee.org. \url{https://doi.org/10.1109/WSC.2011.6147858}

\bibitem[\citeproctext]{ref-Jackson2017-dv}
Jackson, D., \& Turner, R. (2017). Power analysis for random-effects meta-analysis. \emph{Res. Synth. Methods}, \emph{8}(3), 290--302. \url{https://doi.org/10.1002/jrsm.1240}

\bibitem[\citeproctext]{ref-Klein2018-he}
Klein, R. A., Vianello, M., Hasselman, F., Adams, B. G., Adams, R. B., Jr, Alper, S., \ldots{} Nosek, B. A. (2018). Many labs 2: Investigating variation in replicability across samples and settings. \emph{Adv. Methods Pract. Psychol. Sci.}, \emph{1}(4), 443--490. \url{https://doi.org/10.1177/2515245918810225}

\bibitem[\citeproctext]{ref-Knapp2003-qx}
Knapp, G., \& Hartung, J. (2003). Improved tests for a random effects meta-regression with a single covariate. \emph{Stat. Med.}, \emph{22}(17), 2693--2710. \url{https://doi.org/10.1002/sim.1482}

\bibitem[\citeproctext]{ref-Laird1990-ro}
Laird, N. M., \& Mosteller, F. (1990). Some statistical methods for combining experimental results. \emph{Int. J. Technol. Assess. Health Care}, \emph{6}(1), 5--30. \url{https://doi.org/10.1017/s0266462300008916}

\bibitem[\citeproctext]{ref-Lakens2013-eq}
Lakens, D. (2013). Calculating and reporting effect sizes to facilitate cumulative science: A practical primer for t-tests and {ANOVAs}. \emph{Front. Psychol.}, \emph{4}, 863. \url{https://doi.org/10.3389/fpsyg.2013.00863}

\bibitem[\citeproctext]{ref-Lipsey2001-vp}
Lipsey, M. W., \& Wilson, D. B. (2001). Practical meta-analysis. \emph{Applied Social Research Methods Series; Vol 49.}, \emph{247}.

\bibitem[\citeproctext]{ref-Lopez-Lopez2014-it}
López-López, J. A., Marı́n-Martı́nez, F., Sánchez-Meca, J., Van den Noortgate, W., \& Viechtbauer, W. (2014). Estimation of the predictive power of the model in mixed-effects meta-regression: A simulation study. \emph{Br. J. Math. Stat. Psychol.}, \emph{67}(1), 30--48. \url{https://doi.org/10.1111/bmsp.12002}

\bibitem[\citeproctext]{ref-r-lang}
R Core Team. (2022). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing.

\bibitem[\citeproctext]{ref-Rubio-Aparicio2018-pd}
Rubio-Aparicio, M., López-López, J. A., Sánchez-Meca, J., Marín-Martínez, F., Viechtbauer, W., \& Van den Noortgate, W. (2018). Estimation of an overall standardized mean difference in random‐effects meta‐analysis if the distribution of random effects departs from normal. \emph{Res. Synth. Methods}, \emph{9}(3), 489--503. \url{https://doi.org/10.1002/jrsm.1312}

\bibitem[\citeproctext]{ref-Schad2020-ht}
Schad, D. J., Vasishth, S., Hohenstein, S., \& Kliegl, R. (2020). How to capitalize on a priori contrasts in linear (mixed) models: A tutorial. \emph{J. Mem. Lang.}, \emph{110}, 104038. \url{https://doi.org/10.1016/j.jml.2019.104038}

\bibitem[\citeproctext]{ref-Schmid2022-xe}
Schmid, C. H., Stijnen, T., \& White, I. R. (2022). \emph{Handbook of {Meta-Analysis}}. Taylor \& Francis Limited.
